Structural analysis

### 2025-03-20 workflow/notebooks/draft.Rmd
preparing new figs

```{r libraries, message=FALSE, warning=FALSE, cache=FALSE}
library(tidyverse)
library(patchwork)
library(ggtree)
library(cowplot)
library(glue)
library(ggh4x)
source("workflow/scripts/functions.R")
theme_set(theme_classic(base_family = "Helvetica"))

@@

```{r read_trees}
models_draft <- setdiff(models, c("QT", "FTPY", "AF", "LLM"))

df_trees <- read_delim(paste0(params$outdir, 'phylogeny/',
                              params_dataset$phylo_dataset,  "/trees/", 
                              params_dataset$seed, "_unrooted_trees.txt"),
                       show_col_types = FALSE,
                       col_names = c("gene", "target", "alphabet", "model", "tree")) %>% 
  mutate(model=factor(model, levels=models)) %>% 
  filter(!is.na(tree)) %>% #, model %in% models_draft) 
  # some FM trees have negative branch lengths
  mutate(tree = gsub(":-", ":", tree)) 
# 722*8*4=23104 trees

@@

disco_fls <- list.files(paste0(params$outdir, 'phylogeny/',
                              params_dataset$phylo_dataset,  "/reco/disco"), 
                        pattern = "*output*", full.names = T)

@@

# Reconciliation ranger+TCS scores
# glue("results/phylogeny/", params_dataset$phylo_dataset, "/reco/", params_dataset$seed, "_notung.tsv")
reco <- read_delim(paste0(params$outdir, 'phylogeny/',
                              params_dataset$phylo_dataset,  "/reco/", 
                              params_dataset$seed, "_notung.tsv"), 
                   show_col_types = FALSE, 
                   col_names = c("gene", "target", "alphabet", "model", "dups", "losses")) %>% 
  left_join(n_tips) %>% 
  left_join(var_df) %>% 
  mutate(model=factor(model, levels=models),
         n_events = (dups+losses)/n_tips) %>% 
  # filter(model %in% models_draft) %>% 
  rename("targets"="target")

apro_files <- list.files(paste0(params$outdir, 'phylogeny/',
                              params_dataset$phylo_dataset,  "/reco/apro"), 
                        pattern = "*support.nwk", full.names = TRUE)

@@

save.image(file = "workflow/notebooks/eda_cache/until_dftree.Rdata")

knitr::knit_exit()
```

```{r fig3}
xax <- ifelse(df_model$algorithm=="Distance", "italic", "plain")

plot_DL <- reco %>% 
  left_join(df_model) %>% 
  ggplot(aes(weave_factors(model, data), n_events, 
             color=algorithm, fill=targets)) + 
  labs(y="(D+L)/# Tips", x="",fill="Target sets") +
  geom_boxplot(outlier.size = .1) +
  scale_color_manual(values = c("black", "black"),
                     labels = c("ML", expression(italic("Distance")))) +
  guides(x = "axis_nested", 
         colour=guide_legend(title = "Method", override.aes=list(linetype = 0, size=0))) +
  scale_fill_manual(values = palettes_method) +
    theme(
    axis.text.x = element_text(face = xax),
    ggh4x.axis.nestline.x = element_line(color="grey"),
    ggh4x.axis.nesttext.x = element_text(colour = "grey30", 
                                         face = "bold", size=10)
  )

plot_rf <- disco_rf %>% 
  mutate(model=factor(model, levels=models)) %>% 
  filter(nsps>length(sptree$tip.label)/2, model %in% models_draft) %>%
  # separate(bn, c("seed", "targets", "alphabet", "model")) %>% 
  left_join(df_model) %>% 
  ggplot(aes(weave_factors(model, data), rf, 
             color=algorithm, fill=target)) + 
  labs(x="", y="Norm. RF to species tree", fill="Target sets") +
  geom_boxplot(outlier.size = .1) +
  scale_color_manual(values = c("black", "black"),
                     labels = c("ML", expression(italic("Distance")))) +
  guides(x = "axis_nested", 
         colour=guide_legend(title = "Method", override.aes=list(linetype = 0, size=0))) +
  scale_fill_manual(values = palettes_method) +
    theme(
    axis.text.x = element_text(face = xax),
    ggh4x.axis.nestline.x = element_line(color="grey"),
    ggh4x.axis.nesttext.x = element_text(colour = "grey30", 
                                         face = "bold", size=10)
  )

plot_apro <- trees_df %>% 
  left_join(df_model) %>% 
  ggplot(aes(weave_factors(model, data), q1, 
             color=algorithm,fill=targets)) + 
  labs(x="", y="Quartet support", fill="Target sets") + 
  geom_boxplot(outlier.size = .1) +
  scale_color_manual(values = c("black", "black"),
                     labels = c("ML", expression(italic("Distance")))) +
  guides(x = "axis_nested", 
         colour=guide_legend(title = "Method", 
                             override.aes=list(linetype = 0, size=0))) +
  scale_fill_manual(values = palettes_method) +
    theme(
    axis.text.x = element_text(face = xax),
    ggh4x.axis.nestline.x = element_line(color="grey"),
    ggh4x.axis.nesttext.x = element_text(colour = "grey30", 
                                         face = "bold", size=10)
  )

fig3 <- plot_rf + plot_apro + plot_DL +
  plot_layout(guides = "collect") +
  plot_annotation(tag_levels = "A") & 
  theme(plot.tag = element_text(size = 10, face = "bold", family = "Helvetica"),
        legend.position="bottom",
        legend.margin=margin(0,0,0,0),
        legend.box.margin=margin(-25,0,-10,0))

ggsave("draft/figures/Fig3.pdf", fig3, width = 9, height = 2.8, device = cairo_pdf)
```

```{r fig3_sig}
dl_sig <- reco %>% 
  rename("y"="n_events") %>% 
  plot_stat() + 
  labs(y="DL")

disco_sig <- disco_rf %>% 
  mutate(model=factor(model, levels=models)) %>% 
  filter(nsps>length(sptree$tip.label)/2, model %in% models_draft) %>%
  # separate(bn, c("seed", "targets", "alphabet", "model")) %>% 
  left_join(df_model) %>% 
  rename("y"="rf", "targets"="target") %>% 
  plot_stat() + 
  labs(y="RF")

apro_sig <- trees_df %>% 
  select(-y) %>% 
  left_join(df_model) %>% 
  rename("y"="q1") %>% 
  plot_stat() + 
  labs(y="q1")

(disco_sig | apro_sig | dl_sig) + 
  patchwork::plot_layout(guides = "collect") & 
  theme(legend.position = "bottom")
```

@@

# ```{r FigS2}
# pp1_plot <- nodes_df %>%
#     filter(model!="FTPY") %>% 
#     ggplot(aes(q1, label_int, fill=model, color=model, group=model)) +
#     geom_linerange(aes(x=x, xmin=xmin, xmax=xmax, color=model),
#                    data = . %>% 
#                      group_by(model, label_int) %>% 
#                      summarise(x=mean(q1), xmin=min(q1), xmax=max(q1)),
#                    position = position_dodge(width=.7), color="grey70") +
#     geom_point(aes(shape=targets),
#                position = position_dodge(width=.7)) +
#   scale_fill_manual(values=palettes_model) +
#   scale_color_manual(values = palettes_model_d) +
#   scale_shape_manual(values = c(21,22,23,24)) +
#   labs(y="Node") +
#   guides(color = guide_legend(override.aes = list(pch = 21, size=3)),
#          shape = guide_legend(override.aes = list(size=3))) +
#   theme(legend.position = "bottom", legend.box="vertical") + 
#   theme_bw()
# 
# labeled_sptree <- sptree
# labeled_sptree$tip.label <- tax$Species[match(labeled_sptree$tip.label, tax$mnemo)]
# 
# sptree_plot <- ggtree(labeled_sptree) + 
#   geom_tiplab(aes(label=sub("[^A-Z].+? ", ". ", label)),fontface="italic",
#               align = TRUE) + 
#   geom_nodelab(color="firebrick", 
#                nudge_x = -.15, hjust = 1, 
#                nudge_y = .3, size=3.5)+
#   xlim(c(-4, 21))
# 
# fig_s2 <- (sptree_plot + pp1_plot) +
#   plot_layout(widths = c(1, 1.5)) +
#   plot_annotation(tag_levels = 'A') &
#   theme(plot.tag = element_text(size = 10, face = "bold", family = "Helvetica"))
# ggsave("draft/figures/figS2.pdf", fig_s2, width = 12, height = 6, device = cairo_pdf)
<!-- ``` -->

@@

```{r why_no_exp}

plot_PDB <- threed_df %>%
  group_by(mnemo) %>% 
  filter(!is.na(mnemo)) %>% 
  summarise_all(~ (1-sum(is.na(.))/n())*100) %>% 
  left_join(select(tax, mnemo, Species)) %>% 
  ggplot(aes(PDB, fct_reorder(Species, PDB))) + 
  geom_text(aes(label=signif(PDB,2)), family="Aptos", 
            size=2.5, nudge_x = 1, hjust = 0) + 
  geom_bar(stat="identity") + 
  scale_x_continuous(limits = c(0,100), expand = expansion(add = c(0,2))) +
  labs(y="Species", x="% Proteins with PDB entry") + 
  theme(axis.text.y = element_text(face = "italic"))

ggsave("draft/figures/review_nopdb.png", plot_PDB, width = 4, height = 3, dpi = 600)
```

@@

overlap_df %>% 
  mutate(is_not0 = overlap>0) %>% 
  count(set.x, is_not0) %>% 
  pivot_wider(names_from = is_not0, values_from = n) %>% 
  mutate(proportion = `TRUE`/(`FALSE`+`TRUE`)*100)

```

@@

```{r cxx_models}
times_df <- read_delim("tmp.txt", 
                       col_names = c("basename","s","h:m:s","max_rss",
                                     "max_vms","max_uss","max_pss",
                                     "io_in","io_out","mean_load","cpu_time")) %>% 
  mutate(max_rss_gb = max_rss/1024, basename=gsub(".txt", "", basename)) %>% 
  separate(basename, c("seed", "gene", "targets", "alphabet", "model"), sep = "_") %>% 
  select(gene, targets, model, s, `h:m:s`, max_rss_gb)

plot_time_cxx <- times_df %>% 
  # filter() %>% 
  ggplot(aes(fct_reorder(model, s), s/3600)) + 
  geom_boxplot(outlier.size = .1) +
  # scale_y_log10() + 
  scale_y_continuous(transform = "log10")

```

@@

pfam_jaccard %>% 
  mutate(qcov = rowMeans(select(., qcov_Blast, qcov_Foldseek), na.rm = TRUE)) %>% 
  mutate(disc=cut(qcov, breaks = seq(0,100,25))) %>% 
  ggplot(aes(jaccard, disc, color=singleton)) + 
  geom_boxplot() + 
  scale_color_manual(values=palette_singleton_p)

query_pfam <- pfam_jaccard %>% 
  # filter(query=="AF-P06681-F1") %>% 
  group_by(query) %>% 
  summarise(#all_domains = paste0(target_set, collapse = ""),
            q_domains = paste0(unique(query_set), collapse = "")) %>% 
  separate(q_domains, letters, sep = ";")  %>% 
  pivot_longer(cols = !c(query), values_drop_na = T)  %>% 
  filter(value!="") %>% 
  select(-name)

top_pfam <- pfam_jaccard %>% 
  # filter(query=="AF-P06681-F1") %>%
  select(query, target_set)  %>% 
  left_join(query_pfam, relationship = "many-to-many") %>% 
  mutate(is_in = str_detect(target_set, value)) %>%
  group_by(query, value) %>% 
  summarise(n = sum(is_in)) %>% 
  slice_max(n, with_ties = FALSE)

prop_topdomain <- pfam_jaccard %>% 
  # filter(query=="AF-A0A024RCN7-F1") %>% 
  select(query, target_set, singleton) %>% 
  left_join(top_pfam) %>% 
  mutate(is_in = str_detect(target_set, value)) %>% 
  group_by(query, singleton) %>% 
  mutate(n_group = n()) %>% 
  summarise(n = sum(is_in)/mean(n_group))

prop_topdomain %>% 
  ggplot(aes(n, singleton)) + 
  geom_boxplot() + 
  labs(x="% with top domain")
```

>>>>

```{r libraries, message=FALSE, warning=FALSE, cache=FALSE}
library(tidyverse)
library(patchwork)
library(ggtree)
library(cowplot)
library(glue)
library(ggh4x)
library(ggpubr)
library(rstatix)
source("workflow/scripts/functions.R")
theme_set(theme_classic(base_family = "Helvetica"))

@@

```{r read_trees}
models_draft <- setdiff(models, c("QT", "FTPY", "FMG", "C10", "C60"))

unrooted_trees <- paste0(params$outdir, 'phylogeny/',
                              params_dataset$phylo_dataset,  "/trees/", 
                              params_dataset$seed, "_unrooted_trees.txt")
unrooted_trees <- "test/flashforward/out/unrooted_trees.txt"

disco_folder <- paste0(params$outdir, 'phylogeny/',
                              params_dataset$phylo_dataset,  "/reco/disco")
disco_folder <- "test/flashforward/reco/"

notung <- paste0(params$outdir, 'phylogeny/',
                              params_dataset$phylo_dataset,  "/reco/", 
                              params_dataset$seed, "_notung.tsv")
notung <- "test/flashforward/out/notung.txt"

apro_folder <- paste0(params$outdir, 'phylogeny/',
                              params_dataset$phylo_dataset,  "/reco/apro")
apro_folder <- "test/flashforward/reco/"

df_trees <- read_delim(unrooted_trees,
                       show_col_types = FALSE,
                       col_names = c("gene", "target", "alphabet", "model", "tree")) %>% 
  mutate(model=factor(model, levels=models)) %>% 
  filter(!is.na(tree)) %>% #, model %in% models_draft) 
  # some FM trees have negative branch lengths
  mutate(tree = gsub(":-", ":", tree)) 
# 722*8*4=23104 trees

@@

disco_fls <- list.files(disco_folder, 
                        pattern = "*output*", full.names = T)
disco_fls <- list.files(disco_folder, 
                        pattern = "^disco", full.names = T)

@@

# Reconciliation ranger+TCS scores
reco <- read_delim(notung, 
                   show_col_types = FALSE, 
                   col_names = c("gene", "target", "alphabet", "model", "dups", "losses")) %>% 
  left_join(n_tips) %>% 
  left_join(var_df) %>% 
  mutate(model=factor(model, levels=models),
         n_events = (dups+losses)/n_tips) %>% 
  # filter(model %in% models_draft) %>% 
  rename("targets"="target")

apro_files <- list.files(apro_folder, 
                        pattern = "*support.nwk", full.names = TRUE)
apro_files <- list.files(apro_folder, 
                        pattern = "^apro", full.names = TRUE)

@@

save.image(file = "workflow/notebooks/eda_cache/until_dftree.Rdata")
```

```{r fig3}
xax <- ifelse(df_model[df_model$model %in% models_draft,]$algorithm=="Distance", "italic", "plain")

DL_df <- reco %>% 
  left_join(df_model) %>% 
  filter(model %in% models_draft) %>% 
  rename("y"="n_events")
DL_test <- stat_test(DL_df, paired = T, alt = "l")

plot_DL <- DL_df %>% 
  ggplot(aes(weave_factors(model, data), y, 
             color=algorithm, fill=targets)) + 
  labs(y="(D+L)/# Tips", x="",fill="Target sets") +
  geom_boxplot(outlier.size = .1) +
  geom_text(aes(label=as.character(p.adj.signif), y=8, x=group2), 
            data = filter(DL_test, p.adj.signif!="ns"), 
            inherit.aes = F, color="grey20") +
  scale_color_manual(values = c("black", "black"),
                     labels = c("ML", expression(italic("Distance")))) +
  guides(x = "axis_nested", 
         colour=guide_legend(title = "Method", override.aes=list(linetype = 0, size=0))) +
  scale_fill_manual(values = palettes_method) +
    theme(
    axis.text.x = element_text(face = xax),
    ggh4x.axis.nestline.x = element_line(color="grey"),
    ggh4x.axis.nesttext.x = element_text(colour = "grey30", 
                                         face = "bold", size=10)
  )

RF_df <- disco_rf %>% 
  mutate(model=factor(model, levels=models)) %>% 
  filter(nsps>length(sptree$tip.label)/2, model %in% models_draft) %>%
  # separate(bn, c("seed", "targets", "alphabet", "model")) %>% 
  left_join(df_model) %>% 
  rename("y"="rf")
RF_test <- stat_test(RF_df, paired = F, alt = "l")

plot_rf <- RF_df %>% 
  ggplot(aes(weave_factors(model, data), y, 
             color=algorithm, fill=targets)) + 
  geom_boxplot(outlier.size = .1) +
  geom_text(aes(label=as.character(p.adj.signif), y=1.05, x=group2), 
            data = filter(RF_test, p.adj.signif!="ns"), 
            inherit.aes = F, color="grey20") +
  labs(x="", y="Norm. RF to species tree", fill="Target sets") +
  scale_color_manual(values = c("black", "black"),
                     labels = c("ML", expression(italic("Distance")))) +
  guides(x = "axis_nested", 
         colour=guide_legend(title = "Method", override.aes=list(linetype = 0, size=0))) +
  scale_fill_manual(values = palettes_method) +
    theme(
    axis.text.x = element_text(face = xax),
    ggh4x.axis.nestline.x = element_line(color="grey"),
    ggh4x.axis.nesttext.x = element_text(colour = "grey30", 
                                         face = "bold", size=10)
  )

apro_df <- trees_df %>% 
  left_join(df_model) %>% 
  select(-y) %>% 
  filter(model %in% models_draft) %>% 
  rename("y"="q1")
apro_test <- stat_test(apro_df, paired = T, alt = "g")

plot_apro <- apro_df %>% 
  ggplot(aes(weave_factors(model, data), y, 
             color=algorithm,fill=targets)) + 
  labs(x="", y="Quartet support", fill="Target sets") + 
  geom_boxplot(outlier.size = .1) +
  geom_text(aes(label=as.character(p.adj.signif), y=1.05, x=group2), 
            data = filter(apro_test, p.adj.signif!="ns"), 
            inherit.aes = F, color="grey20") +
  scale_color_manual(values = c("black", "black"),
                     labels = c("ML", expression(italic("Distance")))) +
  guides(x = "axis_nested", 
         colour=guide_legend(title = "Method", 
                             override.aes=list(linetype = 0, size=0))) +
  scale_fill_manual(values = palettes_method) +
    theme(
    axis.text.x = element_text(face = xax),
    ggh4x.axis.nestline.x = element_line(color="grey"),
    ggh4x.axis.nesttext.x = element_text(colour = "grey30", 
                                         face = "bold", size=10)
  )

fig3 <- plot_rf + plot_apro + plot_DL +
  plot_layout(guides = "collect") +
  plot_annotation(tag_levels = "A") & 
  theme(plot.tag = element_text(size = 10, face = "bold", family = "Helvetica"),
        legend.position="bottom",
        legend.spacing.x = unit(2, 'cm'),
        legend.margin=margin(0,0,0,0),
        legend.box.margin=margin(-25,0,-10,0))

ggsave("draft/figures/Fig3.pdf", fig3, width = 9.5, height = 2.8, device = cairo_pdf)
```

@@

```{r figs4}
plot_PDB <- threed_df %>%
  group_by(mnemo) %>% 
  filter(!is.na(mnemo)) %>% 
  summarise_all(~ (1-sum(is.na(.))/n())*100) %>% 
  left_join(select(tax, mnemo, Species)) %>% 
  ggplot(aes(PDB, fct_reorder(Species, PDB))) + 
  geom_text(aes(label=signif(PDB,2)), 
            size=2.5, nudge_x = 1, hjust = 0) + 
  geom_bar(stat="identity") + 
  scale_x_continuous(limits = c(0,100), expand = expansion(add = c(0,2))) +
  labs(y="Species", x="% Proteins with PDB entry") + 
  theme(axis.text.y = element_text(face = "italic"))

ggsave("draft/figures/Fig_S4.pdf", plot_PDB, width = 4, height = 3, device=cairo_pdf)
```

@@

@@

overlap_df %>% 
  mutate(is_not0 = overlap>0) %>% 
  count(set.x, is_not0) %>% 
  pivot_wider(names_from = is_not0, values_from = n) %>% 
  mutate(proportion = `TRUE`/(`FALSE`+`TRUE`)*100)
```

@@

```{r cxx_models}
models_cxx <- c("LG", "C10", "C60", "FM", "FMG")
times_df <- read_delim("test/flashforward/times.txt") %>% 
  mutate(max_rss_gb = max_rss/1024) %>% 
  separate(file, c("seed", "gene", "targets", "alphabet", "model"), sep = "_") %>% 
  select(gene, targets, model, s, `h:m:s`, max_rss_gb)

seeds_all <- filter(df_trees, model=="C60") %>% pull(gene)

plot_time_cxx <- times_df %>% 
  # filter() %>% 
  ggplot(aes(fct_reorder(model, s), s/3600)) + 
  geom_boxplot(outlier.size = .1) +
  labs(x="", y="# hours")

plot_mem_cxx <- times_df %>% 
  ggplot(aes(fct_reorder(model, max_rss_gb), max_rss_gb)) + 
  geom_boxplot(outlier.size = .1) +
  labs(x="", y="Memory usage (GB)")

DL_cxx <- reco %>% 
  left_join(df_model) %>% 
  filter(model %in% models_cxx, targets=="common") %>% 
  ggplot(aes(model, n_events, fill=targets)) + 
  labs(y="(D+L)/# Tips", x="",fill="Target sets") +
  geom_boxplot(outlier.size = .1) + 
  scale_fill_manual(values = palettes_method)

RF_cxx <- disco_rf %>% 
  mutate(model=factor(model, levels=models)) %>% 
  filter(nsps>length(sptree$tip.label)/2, model %in% models_cxx, targets=="common") %>%
  ggplot(aes(model, rf, fill=targets)) + 
  geom_boxplot(outlier.size = .1) +
  labs(x="", y="Norm. RF", fill="Target sets") +
  scale_fill_manual(values = palettes_method)

apro_CXX <- trees_df %>% 
  filter(model %in% models_cxx, targets=="common") %>% 
  ggplot(aes(model, q1, fill=targets)) + 
  labs(x="", y="Quartet support", fill="Target sets") + 
  geom_boxplot(outlier.size = .1) +
  scale_fill_manual(values = palettes_method)

fig_CXX <- (RF_cxx + apro_CXX + DL_cxx + plot_mem_cxx + plot_time_cxx)
fig_CXX <-  fig_CXX +
  plot_layout(guides = "collect", nrow = 1, 
              widths = c(5,5,5,3,3)) +
  plot_annotation(tag_levels = "A") &
  theme(legend.position = "none")

ggsave("draft/figures/review_CXX.pdf", fig_CXX, width = 9.5, height = 2.8, device = cairo_pdf)
```

@@

plot_pfam_qcov <- pfam_jaccard %>% 
  mutate(qcov = rowMeans(select(., qcov_Blast, qcov_Foldseek), na.rm = TRUE)) %>% 
  mutate(disc=cut(qcov, breaks = seq(0,100,25))) %>% 
  ggplot(aes(jaccard, disc, color=singleton)) + 
  geom_boxplot(outlier.size = .1) +
  labs(y="Q. cov. interval", x="Pfam JI") +
  scale_color_manual(values=palette_singleton_p)

ggsave("draft/figures/review_qcov.pdf", plot_pfam_qcov, width = 5, height = 6, device = cairo_pdf)

# query_pfam <- pfam_jaccard %>% 
#   # filter(query=="AF-P06681-F1") %>% 
#   group_by(query) %>% 
#   summarise(#all_domains = paste0(target_set, collapse = ""),
#             q_domains = paste0(unique(query_set), collapse = "")) %>% 
#   separate(q_domains, letters, sep = ";")  %>% 
#   pivot_longer(cols = !c(query), values_drop_na = T)  %>% 
#   filter(value!="") %>% 
#   select(-name)
# 
# top_pfam <- pfam_jaccard %>% 
#   # filter(query=="AF-P06681-F1") %>%
#   select(query, target_set)  %>% 
#   left_join(query_pfam, relationship = "many-to-many") %>% 
#   mutate(is_in = str_detect(target_set, value)) %>%
#   group_by(query, value) %>% 
#   summarise(n = sum(is_in)) %>% 
#   slice_max(n, with_ties = FALSE)
# 
# prop_topdomain <- pfam_jaccard %>% 
#   # filter(query=="AF-A0A024RCN7-F1") %>% 
#   select(query, target_set, singleton) %>% 
#   left_join(top_pfam) %>% 
#   mutate(is_in = str_detect(target_set, value)) %>% 
#   group_by(query, singleton) %>% 
#   mutate(n_group = n()) %>% 
#   summarise(n = sum(is_in)/mean(n_group))
# 
# prop_topdomain %>% 
#   ggplot(aes(n, singleton)) + 
#   geom_boxplot() + 
#   labs(x="% with top domain")
```
